[dcpo_gender_roles]: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles

### 2020-10-19 paper/dcpo_gender_roles.Rmd
adding lines
add lines

To overcome this limitation, we develop a comparable cross-national over time measure about gender egalitarian view through the DCPO package for R [@Solt2020a]. (Quick Review of our Index can be included).

@@

Even though questionnaires in the four categories are asking about opinions about gender roles, generating a measure of egalitarian gender roles without the classification may cause multidimensionality problem since people might have different opinions about gender roles by the dimensions.
For instance, some people have a more egalitarian veiw about the gender role in public sector rather than in private sector, while others do not.

>>>>

To overcome this limitation, we develop a comparable cross-national over time measure about gender egalitarian view in the public sector through the DCPO package for R [@Solt2020a]. (Quick Review of our Index can be included - number of countries and years, unit of analysis, number of surveys and questionnaires will be introduced).

@@

Even though questionnaires in the four categories are asking about opinions about gender roles, generating a measure of egalitarian gender roles without the classification may cause multidimensionality problem since people might have different opinions about gender roles by the dimensions.
For instance, some people have a more egalitarian veiw about the gender role in public sector rather than in private sector, while others do not.
Given that the number of questionnaires about gender roles is relatively high compared to others (I think adding the actual numbers will be helpful), we focus on the opinions about gender role in public sectors to generate our estimate of egalitarian gender role.
